\chapter{Literature Review}

In this chapter I will demonstrate some of the extended citation
capabilities provided by the {\sf Harvard} package \cite{WiS1994}. As well
as supporting the standard \LaTeX\ \verb+\cite+ command, it provides a
few other very useful ones.

The \verb+\cite+ command is best used when placing a citation at the end of
sentence or phrase (as above). When you want to refer to the authors of a
particular work, typically at the start of a sentence, \verb+\cite+ is not
appropriate. This is particularly so if you are using a numerical or
symbolic citation style. You should \emph{not} start a sentence with
\begin{quote}
[2] says that this is most certainly \ldots
\end{quote}
In such situations you really need to give the authors' names. The {\sf
Harvard} package provides a new command \verb+\citeasnoun+, which allows
you to produce things like:
\begin{quote}
\citeasnoun{Ade1983} describes a means by which textures may be
characterized \ldots another approach is given in \citeasnoun{DeV1998}.

\citeasnoun{AGR1996} note that humans have little or no difficulty in
perceiving shape, yet find it extremely difficult to \emph{describe} what
they perceive.
\end{quote}

Another useful new command provided by the {\sf Harvard} package is
\verb+\possessivecite+. This is used when you want to use the authors in a
possessive sense, as below:
\begin{quote}
\possessivecite{AGR1996} experiments with hundreds of three-dimensional scans of human heads suggests that \ldots
\end{quote}
Note that an abbreviated version of the authors' names has been used above.
The {\sf Harvard} package does this automatically after the first citation.
This behaviour can be overridden if desired.

\paragraph{Note:} The standard {\sf Harvard} package is incompatible with
\texttt{pdflatex} (via the {\sf html} package). If you want to use the {\sf
Harvard} package with \texttt{pdflatex}, make sure you use the version
supplied here (2.0.5a), which has been hacked to remove the problem.

In the long run, {\sf natbib} is probably the better choice. Watch this
space...
